Variation in gaze understanding across the life span: A process-level perspective

### 2023-06-15 paper/manuscript.Rmd
update magnet data (remove safety copies), add suppl. human vs animal stimuli analysis

The remote child and teenager sample consisted of `r sum(lifespan_sample$n_total[lifespan_sample$age_group < 18])` children, including `r lifespan_sample$n_total[lifespan_sample$age_group == "3"]` 3-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "3"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "3"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "3"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "3"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "3"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "4"]` 4-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "4"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "4"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "4"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "4"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "4"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "5"]` 5-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "5"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "5"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "5"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "5"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "5"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "6"]` 6-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "6"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "6"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "6"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "6"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "6"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "7"]` 7-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "7"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "7"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "7"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "7"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "7"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "8"]` 8-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "8"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "8"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "8"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "8"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "8"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "9"]` 9-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "9"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "9"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "9"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "9"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "9"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "10"]` 10-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "10"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "10"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "10"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "10"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "10"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "11"]` 11-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "11"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "11"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "11"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "11"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "11"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "12"]` 12-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "12"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "12"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "12"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "12"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "12"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "13"]` 13-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "13"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "13"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "13"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "13"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "13"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "14"]` 14-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "14"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "14"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "14"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "14"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "14"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "15"]` 15-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "15"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "15"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "15"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "15"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "15"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "16"]` 16-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "16"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "16"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "16"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "16"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "16"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "17"]` 17-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "17"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "17"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "17"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "17"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "17"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "18"]` 17-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "18"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "18"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "18"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "18"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "18"]` girls), `r lifespan_sample$n_total[lifespan_sample$age_group == "19"]` 17-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "19"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "19"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "19"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "19"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "19"]` girls).

Children and teenagers in our sample grow up in an industrialized, urban Central-European context. Information on socioeconomic status was not formally recorded, although the majority of families come from mixed, mainly mid to high socioeconomic backgrounds with high levels of parental education.

Adults were recruited via *Prolific* [@palan2018prolific]. *Prolific* is an online participant recruitment service from the University of Oxford with a predominantly European and US-American subject pool. Participants consisted of `r sum(lifespan_sample$n_total[lifespan_sample$age_group >= 20])` English-speaking adults that reported to have normal or corrected-to-normal vision. The sample included `r lifespan_sample$n_total[lifespan_sample$age_group == "20"]` 20- to 29-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "20"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "20"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "20"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "20"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "20"]` female), `r lifespan_sample$n_total[lifespan_sample$age_group == "30"]` 30- to 39-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "30"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "30"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "30"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "30"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "30"]` female), `r lifespan_sample$n_total[lifespan_sample$age_group == "40"]` 40- to 49-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "40"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "40"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "40"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "40"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "40"]` female), `r lifespan_sample$n_total[lifespan_sample$age_group == "50"]` 50- to 59-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "50"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "50"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "50"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "50"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "50"]` female), `r lifespan_sample$n_total[lifespan_sample$age_group == "60"]` 60- to 69-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "60"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "60"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "60"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "60"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "60"]` female), and `r lifespan_sample$n_total[lifespan_sample$age_group == "70"]` 70- to 79-year-olds (mean = `r lifespan_sample$age_mean[lifespan_sample$age_group == "70"]` years, SD = `r lifespan_sample$age_sd[lifespan_sample$age_group == "70"]`, range = `r lifespan_sample$age_min[lifespan_sample$age_group == "70"]` - `r lifespan_sample$age_max[lifespan_sample$age_group == "70"]`, `r lifespan_sample$n_females[lifespan_sample$age_group == "70"]` female).

@@

As in the two previously reported studies, we presented children with the continuous version of the TANGO [@prein2022tango]. Children were tested on a tablet.

>>>>

The remote child and teenager sample consisted of `r sum(lifespan_sample$n_total[lifespan_sample$age_group < 18])` participants. Children and teenagers in our sample grow up in an industrialized, urban Central-European context. Information on socioeconomic status was not formally recorded, although the majority of families come from mixed, mainly mid to high socioeconomic backgrounds with high levels of parental education.

Adults were recruited via *Prolific* [@palan2018prolific]. *Prolific* is an online participant recruitment service from the University of Oxford with a predominantly European and US-American subject pool. Participants consisted of `r sum(lifespan_sample$n_total[lifespan_sample$age_group >= 20])` English-speaking adults that reported to have normal or corrected-to-normal vision. For further information on age and gender of participants, see Table 1.

@@

Children were tested on a tablet. As in the two previously reported studies, we presented children with the continuous version of the TANGO [@prein2022tango]. 
To accentuate the social aspect of the gaze understanding task, we exchanged the animal agents (used in the previous two studies) with human faces, which were modeled after the local population in appearance. This further highlighted the contrast to the non-social vector estimation task. We had already created these stimuli for another project focusing on cross-cultural similarities in gaze understanding (https://osf.io/tdsvc). [^1]

[^1]: In an exploratory analysis, we compared children's imprecision levels in the TANGO task with animal vs. human agents. Based on a GLMM analysis, we conclude that there was no evidence of a stable effect of stimulus choice (human vs. animal). See Supplements for further detail.
